---
title: "Introduction"
author: "Eugénie Mathieu"
date: "26 12 2020"
output: html_document
---

```{r, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(kableExtra)

```

# Introduction

With 57 millions of Tinder users worldwide, the dating app Tinder had been a trend until becoming a robust daily service mostly used by young adults. An extensive scientific litterature investigate Tinder an its uses. Typical dating apps, and mostly Tinder, rely on objectification theory (Strubel and Petrie, 2017), which supports that Tinder represents a contemporary medium for appearance pressures and its use is associated with a variety of negative perceptions about body and self and with increases in individuals’ likelihood to internalize appearance ideals and make comparisons to others. Path analysis showed that self-esteem mediated the effect of social media addiction on satisfaction with life (Hawi and Samaha, 2016). Self-esteem is defined by a total of the individual's thoughts and feelings with reference to himself as an object (Rosenberg, 1965). Self-esteem enhancement motivation to use Tinder consistently showed an important role in the development and maintenance of problematic Tinder use compared to the effects of personality traits Personality has a minor role in behavioral addictions. However, self-determination theory-based need frustrations are more relevant background variables of problematic online behaviors (Orosz et al., 2018) Moreover, impulsive people may be drawn to dating apps due to the speed with which they can rate people. Impulsiveness has been linked to a variety of risky behaviors (Stanford, et al., 1996) and may be connected to both using the app extensively and quickly meeting people one meets on dating apps. The research conveys a lot of hypothesis and directions to take for further investigations.


Conversations and animated debates are created by experiences via this application at the University of Lausanne and beyond, and Tinder announced during the second quarter that the pandemic has increased the number of active users. In troubled times as we have known in 2020, it is interesting to investigate the current use of Tinder among 18-26 years old young adults. This experiment is an investigation on self-perception of Tinder users, more precisely what their scores of body acceptance, self-esteem and impulsiveness are and what is the magnitude of change of those scores when we manipulate their self-perception. The measures of those traits are supported by the Rosenberg's Self-Esteem Scale (Winch and Rosenberg, 1965), the Body Acceptance Scale (Avalos, Tylka and Wood-Barcalow, 2005) and the Abbreviated Impulsiveness Scale (Coutlee, Politzer, Hoyle and Huettel, 2014), short surved-based tests in order to limit the overall experiment time. By doing this experiment, the present work aims to obtain cosistent results with respect to the underlying litterature, while better understand the user profiles of the sample and their self-esteem robustness to anegative manipulation. As start hypothesis, we consider here that the Tinder users' scores of self-esteem, body acceptance and impulsivity would be significantly different from non users. We expect to have lower scores in the two first measures and a higher impulsivitiy score. As we expect lower self-esteem score in the Tinder users subset, we  as well expect a high variation of self-esteem when externally manipulated, what would reflect an inconstant image of himself weaken by a lower self-esteem.

The survey-based control Group posttest-only designed experiment is run as follow: a participant is categorized as Tinder users or non User to answer the Tinder Motivation Scale, the Rosenberg S-ES, the BAS ans the AIS during a computer-based test. Non-Users would be the referential for the scores (control group). The Tinder Users would be randomly allocated to the treatments consisting in negative feedbacks sent during the Rosenberg's Scale and an anchoring negative article on self-body image and its cruciality in the pre-dating mindset. 

# Research Question, Definitions and Hypothesis 

The research question is _how does self-esteem, body acceptance & impulsiveness scores model the motive of Tinder use and what are their proprensities to vary?_ It is based on different studies showing that addictive use of social media had a negative association with self-esteem, and the latter had a positive association with satisfaction with life. (Hawi and Samaha, 2016) or that personality plays only a minor role in behavioral addictions. The problematic use of Tinder is not investigated here, but this experience is run in the context of a pandemic, whose consequences might have affected more certain persons who can rely on Tinder for a ego boost (Hawi and Samaha, 2016). This point is supported by studies supporting that self-determination theory-based need frustrations are more relevant background variables of problematic online behaviors such as problematic Tinder use (Orosz et al., 2018). The increasing use of Tinder, mentioned above, may meet needs other than pleasure and entertainment and may be motivated by a variety of social and psychological reasons. Self-esteem is one of the psychological reasons that may be related to the use of Tinder, which will meet a different need if self-esteem is high or low. 

*Self-esteem* is an individual's subjective assessment of his/her own worth. Self-esteem encompasses beliefs about oneself (for example, "I am unloved", "I am worthy") as well as emotional states, such as triumph, despair, pride, and shame. (Hewitt, John P., 2009)

Also, since Tinder is based on a system of representation where the selection of users is based on photos (3 usually, max 9 photos and only 150 characters max for the descrption) and therefore on the physical, the perception of one's body is intrinsically correlated. This is why we decided to study the body acceptance.

*Body image* had been defined by previous researches as a complex, multidimensional construct that includes self-perceptions and attitudes (i.e., thoughts, feelings, and behaviors) with regard to the body (e.g., Cash, Jakatdar, & Williams, 2004; Thompson, Heinberg, Altabe, & Tantleff-Dunn, 1999).Different components composed body image such as (not exhaustive list) appearance evaluation, appearance orientation, body esteem, and accuracy of size perception (Thompson et al., 1999).

Motivations for using Tinder based on a self-perception bias can also be related to impulsiveness, which is why impulsiveness is also studied here.

*Impulsiveness* is a personality trait that reflects an urge to act spontaneously, without thinking or planning ahead for the consequences of your actions. High impulsiveness is characteristic of a variety of problematic behaviorsm implying for example danger seeking and high risk-taking (Coutlee, Politzer, Hoyle and Huettel, 2014). 

To study these three variables, we have chosen three scales of measurement:

* _Tinder Motives Scale (TMS)_ (Timmermans and De Caluwé, 2017): According to this study, 8 motivations were defined to join Tinder. These reasons constitute the levels of our TinderMainMotives feature: social approval, social pressure, information seeking, relationship seeking, passing time, entertaining, sexual experience and socializing. This scale has been adopted by several other researchers, making it a legitimate choice. The questionnaires vary in length and questions, however they overlap in these 8 motivational categories.

* _Rosenberg Self-Esteem scale (SES)_ ( Winch and Rosenberg, 1965): Since 1965, this scale is the reference to define the self-esteem of a subject. Composed of 13 questions bringing between 0 and 3 points, the sum of the points of the questions allows the measurement of the self-esteem. A result lower than 15 marks a (very) low self-esteem, a score between 15 and 25 points out of 30 being regarded as normal. 

* _Body Acceptance scale (BAS)_ (Avalos, Tylka and Wood-Barcalow, 2005): The choice of the BAS was made after reading a study on the robustness of this scale among the multitude of other measures of the body aceptance scale. The questionnaire has 13 positive questions allowing the calculation of an average score between 1 (non-acceptance) and 4 (good body acceptance). 

* _Impulsiveness scale (AIS)_ (Coutlee, Politzer, Hoyle and Huettel, 2014) : Il s'agit d'un questionnaire de 12 questions qui calculent le score de 3 dimensions, Attention, Motor and Future Planning. The initial scale being of a certain length, an abbreviated version was created and Coutlee, Politzer, Hoyle and Huettel assessed in 2014 the sustainable results obtained by this shortest scale. We use here the abbreviated version, in order to keep somehow a similar length among the scales.


Our start hypothesis are the following:

* Non-tinder subset have different scores in BAS, S-ES and AIS
* Significant correlation between Tinder Motive Scales and BAS, S-ES and AIS, and can be used as significant feature for modeling 
* Self-esteem and body acceptance can be manipulated since already low


# Experimental method and sampling

##Experimental design

The present survey-based experiment is created on the Questback platform (licensed), which is an advanced tool for professional surveys as much as academical computer-based experiments. A license was bought. Five pages or questions are displayed: a first page for socio-demographic data collection, after comes the Tinder Motive Scale (TMS), the Rosenberg Self-Esteem Scale (S-ES), the Body Acceptance Scale (BAS) and the Abbreviated Impulsiviness Scale (AIS).

The experiment is run with two control groups* and two experimental groups to have observation on both Tinder Users and Non-Users. Tinder users, which are catergorized as such if they have a Tinder account and use it more than once a month. Non-Users have thus either a non-active account or no account at all. Both Users and Non-Users particpants are randomly allocated to the treatment. It consists in negative feedback during the completion of the S-ES and an negative anchor before the BAS. Negative feedbacks are articifical comparisons with the other participants, aiming to informs on the lower quality performance of the manipulated participant so as to perturbate him. The S-ES are expected to be affected by the treatment, whose measure would outline a greater variation in score than for the control group. For the second treatment, the article on body acceptance, conveys judgements on aesthetics, corpulence, beauty and flaws. Both treatments are based on usual experimental manipulations. Nevertheless, the effects of manipulation by bogus feedbacks is disputed, but it is enough used that to remain an easy option for manipulating self-esteem. For body acceptance score, we use an anchor with the article.

The data collected would help to verify the 1rst hypothesis: a significant difference in scores, and to compare the variation of those scores after treatments.

* `The initial experimental design was adapted as soon as December 18th to find Non-Users so as to participate to the treatment, in order to have a comparison point for the score variation.`

## Sample

The sample was gathered by a non-probabilistic process. The advertisement of the survey consists in Facebook posts and to personnal invitation on Whatsapp (friends and acquaintances). Participants relayed the link to the survey, and without knowing until what extent it has worked, we prefer here to speak about convenience sampling rather than snowball sampling.


```{r load data and cleaning,echo=FALSE,warning=FALSE}

mdata <- read.csv2(here::here("DataTinder.csv"))
qq<-nrow(mdata)
mydata <- mdata %>% filter(Age > 17, Age <27)
pp<-nrow(mydata)

```

Initially composed by `r qq` participants, after cleaning to remove participants not in the target age (18-26), the resulting sample counts `r pp` subjects, distributed as the \@ref(tab:grouptable) shows.
 
```{r grouptable, fig.cap="Participants frequency in groups",echo=FALSE,warning=FALSE, message = FALSE}
mydata %>%
  group_by(Group) %>%
  summarize(n = n()) %>%
kable() %>% kable_styling()

```

To better see the distribution of the age, we use the  \@ref(fig:age-per-group-plot) figure. The age is less well distributed for the experimental group of Non-Users, as it might be expected since this group was created at a late stage of the experiment. It is less representative of the main sample, if we consider the the Non-Users control group as a realistic caption of the population of Tinder Non-Users.

```{r age-per-group-plot, fig.cap="Age per group plot",echo=FALSE,warning=FALSE}
mydata %>%
  group_by(Age, Group) %>%
  summarize(n = n()) %>%
  ggplot(aes(x=Age,y= n,fill = Group)) + 
  geom_bar(stat="identity",alpha=0.8) +
  facet_wrap(~ Group) + 
  coord_flip() +
  ggtitle("Number of participants per Age and per sample subset") +
  xlab("Age of participants") +
  ylab("Number per type") +
   geom_text(aes(label = n), size = 3, hjust = 1, vjust = 0, position = "stack")
```

Our panel is not homogeneously composed by students, but as well by part-timers, fixed employees and three job-seekers ( \@ref(tab:kable-number-socialstatus) ).

```{r kable-number-socialstatus,echo=FALSE,warning=FALSE }
mydata %>%
  group_by(SocialStatus) %>%
  summarize(n = n()) %>%
  kable() %>% kable_styling()
```

Our sample is composed by 70 single participants and 54 participants in a relationship (43.5%). As present plot \@ref(fig:relationship-plot) plot, Non-Users are essentially composed by participants engaged in a relationship or single. We note that they are more inclined to have a traditionnal approach to relationship (binary options): either being in a relatioship where having extra sexual relationships is forbidden or being single. For Tinder Users, the relationship types are more diversified: there are almost twice more of open relationships than closed ones, 16 people have punctual sex/ hookup plans and a majority is single (32 people). Statistics on Tinder informs that the worldwide Tinder users population composed by 54% of single users and 46% in a relationship (Smith, 2020). Our subset is composed by 26.5% participants in a relationship and 73.5% are single.

 !! _Be aware that the below figure present in an inverse order the control and experimental groups of Tinder Users, in comparison to the Non Users_ .

```{r relationship-plot, fig.cap= "relationship-plot", echo=FALSE,warning=FALSE}
mydata %>%
  group_by(Relationship, Group) %>%
  summarize(n = n()) %>%
  ggplot(aes(x=Relationship,y= n,fill = Group)) + 
  geom_bar(stat="identity",alpha=0.8) +
  facet_wrap(Group~.) + 
  coord_flip() +
  ggtitle("Number of participants per type of Relationship and per sample subset") +
  xlab("Type of relationships") +
  ylab("Number of participants per type") +
   geom_text(aes(label = n), size = 3, hjust = 1, vjust = 0, position = "stack")
```





